\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered through Citizen Science

### 2015-05-09 doc/sw-cfhtls.tex
Fixed some small things #203

The parameters required by the models' various scaling relations
primarily depend on the photometry of the galaxies, groups and quasars
detected in the survey. For galaxy-scale lenses, the fainter or higher redshift
lensing galaxies at tend to have poor photometric redshift
measurements. Consequently these galaxies were occasionally assigned the wrong
luminosity and velocity dispersion estimates, resulting in
simulated lenses which look implausible or unrealistic.  For example,
the lensed images for some of the failed simulations have larger image
separation than would be expected from the luminosity and/or size of the
galaxy.

@@

@@

From the SWAP, the image cutouts inspected by the \sw volunteers receive
a status of detected (if P$>$P$_{\rm acc thresh}$), rejected (if
P$<$P$_{\rm rej thresh}$) and undecided (if $P_{\rm rej thresh}< P <
P_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the positions
of lenses which are detected (red), undecided (green) and rejected
(blue). The left and the right panels have the simulated lens sample and
the known lens candidates sample, respectively. We note that the density
of points do not represent the actual number of detections because, for
cases with large sample size, randomly drawn subsamples are shown for
the ease of visual comparison.

@@

We check how the posterior probability $P$ (see \PaperOne for the
mathematical definition) of an image or a subject to contain a lens
changes as the image receives more classifications from multiple
volunteers. A graphical representation of changing probabilities for
increasing classifications is called a trajectory plot. In
\Fref{fig:detmis}, we show the trajectory plots of a few examples of
detected lenses (top left panels) and missed lenses (bottom left panels)
from \StageOne of \sw. The number of classifications (Nclass) for a
subject increase from top to bottom.  Also, every subject is assigned a
prior probability $P_0=2\times10^{-4}$ (grey dashed line) and starts at
the middle of the trajectory plot. The $P$ value of a subject is updated
with every classification from the volunteer.  If a volunteer identifies
a lens candidate, the trajectory moves to the right otherwise moves to
the left. A subject is accepted if it crosses the blue-dashed line
marking the (P$_{\rm acc thresh}=0.95$) on the right and is rejected, if
it crosses the red-dashed line marking the $P_{\rm rej thresh}=10^{-7}$
on the left.

@@

For a quantitative comparison of the large and small kicks for the
entire samples of detected and missed known lenses, we show a plot of
histogram on the right of \Fref{fig:detmis}. Qualitatively, there are
four types of volunteers making classifications - those causing positive
large kicks (correct classifications by high power volunteers, those
causing positive small kicks (correct classifications by low power
volunteers), those causing negative small kicks (incorrect
classifications by low power volunteers) and those causing negative
large kicks (incorrect classifications by high power volunteers). The
four histograms in the figure correspond to these four types of
volunteers for each sample (that is, detected or missed). The kick size
is small if $\Delta$ log(P)$=$log (P$_{\rm current}) - $log(P$_{\rm
previous}) < \Delta$log(P)$_{\rm cut}$ (chosen as 1.2) and is large
if greather than $\Delta$log(P)$_{\rm cut}$.

>>>>

The parameters required by the models' various scaling relations
primarily depend on the photometry of the galaxies, groups and quasars
detected in the survey. For galaxy-scale lenses, the fainter or higher redshift
lensing galaxies tend to have poor photometric redshift
measurements. Consequently these galaxies were occasionally assigned the wrong
luminosity and velocity dispersion estimates, resulting in
simulated lenses which look implausible or unrealistic.  For example,
the lensed images for some of the failed simulations have larger image
separation than would be expected from the luminosity and/or size of the
galaxy.

@@

% PHIL IS HERE

@@

From the SWAP, the image cutouts inspected by the \sw volunteers receive
a status of detected (if $P>P_{\rm acc thresh}$), rejected (if
$P<P_{\rm rej thresh}$) and undecided (if $P_{\rm rej thresh}< P <
P_{\rm acc thresh}$). In \Fref{fig:comppos}, we compare the positions
of lenses which are detected (red), undecided (green) and rejected
(blue). The left and the right panels have the simulated lens sample and
the known lens candidates sample, respectively. We note that the density
of points do not represent the actual number of detections because, for
cases with large sample size, randomly drawn subsamples are shown for
the ease of visual comparison.

@@

We check how the posterior probability $P$ (see \PaperOne for the
mathematical definition) of an image or a subject to contain a lens
changes as the image receives more classifications from multiple
volunteers. A graphical representation of changing probabilities for
increasing classifications is called a trajectory plot. In
\Fref{fig:detmis}, we show the trajectory plots of a few examples of
detected lenses (top left panels) and missed lenses (bottom left panels)
from \StageOne of \sw. The number of classifications (Nclass) for a
subject increase from top to bottom.  Also, every subject is assigned a
prior probability $P_0=2\times10^{-4}$ (grey dashed line) and starts at
the middle of the trajectory plot. The $P$ value of a subject is updated
with every classification from the volunteer.  If a volunteer identifies
a lens candidate, the trajectory moves to the right otherwise moves to
the left. A subject is accepted if it crosses the blue-dashed line
marking the ($P_{\rm acc thresh}=0.95$) on the right and is rejected, if
it crosses the red-dashed line marking the $P_{\rm rej thresh}=10^{-7}$
on the left.

@@

For a quantitative comparison of the large and small kicks for the
entire samples of detected and missed known lenses, we show a plot of
histogram on the right of \Fref{fig:detmis}. Qualitatively, there are
four types of volunteers making classifications - those causing positive
large kicks (correct classifications by high power volunteers, those
causing positive small kicks (correct classifications by low power
volunteers), those causing negative small kicks (incorrect
classifications by low power volunteers) and those causing negative
large kicks (incorrect classifications by high power volunteers). The
four histograms in the figure correspond to these four types of
volunteers for each sample (that is, detected or missed). The kick size
is small if $\Delta log{P} = \log{P_{\rm current}} - \log{P_{\rm
previous}} < \Delta\log{P}_{\rm cut}$ (chosen as 1.2) and is large
if greather than $\Delta\log{P}_{\rm cut}$.
